Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-16 paper/main.tex
intro: add references to annotations

% literature review overview 1: imagination & haptic exploration
Increased hemodynamic activity in the PPA generalizes to mental imagination of
landscapes \citep{ocraven2000mental}, and haptic exploration of scenes
constructed from LEGO blocks \citep{wolbers2011modality}.\todo{cite Lescroart
    \&Gallant, Human Scene-Selective Areas Represent 3D Configurations of
    Surfaces, Neuron, 2019; semi-naturalistic, but not taskfree, 800+ stimulus,
not "a small set", 6 subjects}
% O'Craven: watching pictures
In a study conducted by \cite{ocraven2000mental} participants viewed alternating
blocks of pictures showing familiar places and famous faces during an initial
experimental paradigm.
% O'Craven: mental imagery
In a subsequent paradigm, participants were instructed to ``form a vivid mental
image'' of the previously viewed pictures.
% O'Craven results
The PPA showed increased activation during imagination of places compared to
faces but the imagination tasks showed a smaller activation level compared to
the perceptual task.
% Wolbers: haptic exploration
In a block design study conducted by \cite{wolbers2011modality} the PPA of
sighted as well as blind participants showed increased activation during a
delayed match-to-sample task of haptically explored scenes constructed from LEGO
bricks compared to abstract geometric objects.
% Wolbers: connectivity analysis

@@

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually detected by contrasting blocks of pictures can also be revealed under
more ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual spatial perception is based on an annotation of
cuts and depicted locations in the audio-visual movie ``Forrest Gump'', while
% AD stimulus
non-visual spatial perception is investigated using an annotation of spatial
references in the speech occurring in the movie's audio-description.
% GLM contrasts
We applied whole-brain, model-based, mass-univariate analyses to a series of
datasets with BOLD fMRI data from naturalistic and conventional block-design
stimulation from the same set of participants, available from the open-data
resource \href{http://www.studyforrest.org}{studyforrest.org}
\citep{hanke2016simultaneous, hanke2014audiomovie, sengupta2016extension}.
\todo{cite Häusler \& Hanke 2021}

>>>>

% literature review overview 1: imagination & haptic exploration
Increased hemodynamic activity in the PPA generalizes to mental imagination of
landscapes \citep{ocraven2000mental}, haptic exploration of scenes
constructed from LEGO blocks \citep{wolbers2011modality} and scene-related
sounds \citep{van2017development}.\todo{reading the paper: activation is
non-significant, lol}
% van der Hurk: 64 sounds x 1.8 seconds; 20 sighted, 14 congenitally blind
\todo{cite Lescroart (2019). semi-naturalistic, but task, 800+ stimulus, N=6}
% O'Craven: watching pictures
In a study conducted by \cite{ocraven2000mental} participants viewed alternating
blocks of pictures showing familiar places and famous faces during an initial
experimental paradigm.
% O'Craven: mental imagery
In a subsequent paradigm, participants were instructed to ``form a vivid mental
image'' of the previously viewed pictures.
% O'Craven results
The PPA showed increased activation during imagination of places compared to
faces but the imagination tasks showed a smaller activation level compared to
the perceptual task.
% Wolbers: haptic exploration
In a block design study conducted by \cite{wolbers2011modality} the PPA of
sighted as well as blind participants showed increased activation during a
delayed match-to-sample task of haptically explored scenes constructed from LEGO
bricks compared to abstract geometric objects.
% Wolbers: connectivity analysis

@@

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually detected by contrasting blocks of pictures can also be revealed under
more ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual spatial perception is based on an annotation of
cuts and depicted locations \citep{haeusler2016cutanno} in the audio-visual
movie ``Forrest Gump'', while
% AD stimulus
the operationalization of non-visual spatial perception is based on an
annotation of speech \citep{hausler2021studyforrest} occurring in the movie's
audio-description.
% GLM contrasts
We applied whole-brain, model-based, mass-univariate analyses to a series of
datasets with BOLD fMRI data from naturalistic and conventional block-design
stimulation from the same set of participants, available from the open-data
resource \href{http://www.studyforrest.org}{studyforrest.org}
\citep{hanke2016simultaneous, hanke2014audiomovie, sengupta2016extension}.
\todo{cite Häusler \& Hanke 2021}
